Pilot data analysis

### 2021-03-13 data_analysis_brms_old.Rmd
brms experiment 2 RT

blmm_exp1 <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500, rt ~
Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
warmup = 1000,
iter = 5000,
chains = 4,
prior = prior_exp1,
family = exgaussian(),
inits = "random",
control = list(adapt_delta = 0.95),
cores = 4, backend = "cmdstanr", threads = threading(2))

@@

save(blmm_exp1, file = "blmm_exp1.RData")
```

>>>>

blmm_exp2 <- brm(data = exp2_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), 
                        rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
                        warmup = 1000,
                        iter = 5000,
                        chains = 4,
                        prior = prior_exp1,
                        family = exgaussian(),
                        inits = "random",
                        control = list(adapt_delta = 0.95),
                        cores = 4, backend = "cmdstanr", threads = threading(2))

@@

save(blmm_exp2, file = "blmm_exp2.RData")
```
